Final Project Code ALL

### 2022-11-30 Final_Project_Code_ALL.Rmd
Worked on evaluation metrics and choosing threshold for log model

>>>>

```{r}
# Creation of CV Folds
data_cv10_class <- vfold_cv(imdb_clean_class, v = 10)
```

```{r}
full_log_wf <- workflow() %>%
    add_recipe(logistic_rec) %>%
    add_model(logistic_spec)

log_model <- fit(full_log_wf, data = imdb_clean_class)

log_modelcv <- fit_resamples(full_log_wf, resamples = data_cv10_class, metrics = metric_set(accuracy,sens,yardstick::spec))

log_modelcv %>%
  collect_metrics()
```

```{r}
# Soft Predictions on Training Data
final_output <- log_fit %>% predict(new_data = imdb_clean_class, type='prob') %>% bind_cols(imdb_clean_class)

final_output %>%
  ggplot(aes(x = flop, y = .pred_TRUE)) +
  geom_boxplot()
```

```{r}
# Use soft predictions
final_output %>%
    roc_curve(flop,.pred_TRUE,event_level = 'second') %>%
    autoplot()
```

```{r}
# thresholds in terms of reference level
threshold_output <- final_output %>%
    threshold_perf(truth = flop, estimate = .pred_FALSE, thresholds = seq(0,1,by=.01))

# J-index v. threshold for no flop
threshold_output %>%
    filter(.metric == 'j_index') %>%
    ggplot(aes(x = .threshold, y = .estimate)) +
    geom_line() +
    labs(y = 'J-index', x = 'threshold') +
    theme_classic()
```

```{r}
threshold_output %>%
    filter(.metric == 'j_index') %>%
    arrange(desc(.estimate))
```

```{r}
# Distance v. threshold for not_spam

threshold_output %>%
    filter(.metric == 'distance') %>%
    ggplot(aes(x = .threshold, y = .estimate)) +
    geom_line() +
    labs(y = 'Distance', x = 'threshold') +
    theme_classic()
```

```{r}
threshold_output %>%
    filter(.metric == 'distance') %>%
    arrange(.estimate)
```

```{r}
log_metrics <- metric_set(accuracy,sens,yardstick::spec)

final_output %>%
    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .88)) %>%
    log_metrics(truth = flop, estimate = .pred_class, event_level = 'second')

final_output %>%
  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .88)) %>%
  conf_mat(truth = flop, estimate = .pred_class)
```

*How to add threshold here?*
